Investigation on GIT

### 2010-04-25 paper.tex
expansion de la introduccion

\PARstart

@@

Version Control Systems (VCS) usually track the whole history of the
source code in a central server that everyone that can access. This 
central server contains all the changes and branches of the code and 
the users that can read the versions or commit changes have to connect 
to this repository.
Distributed Version Control Systems (DVCS) are a modern way of managing
revisions of software that do not have a centralized server, for this reason 
they are also called De-centralized Version Control Systems. Everybody has a 
copy of the full repository with all changes made in the history.

Vamos a contar cuando surgió esta tecnología y sus principales 
exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 
similitudes con otros sistemas de versionado distribuidos como Mercurial. 
Un poco se contará las diferencias fundamentales entre las herramientas de 
versionado centralizadas y distribuidas, simplemente nombrando las diferencias 
pero no explicándolas.

La idea del paper sería contar las ventajas que puede 
tener este esquema dentro de un ambiente enterprise de código cerrado, en contraste 
a un ambiente open source donde el esquema distribuido tiene incluso más sentido.

>>>>

@@

\PARstart Version Control Systems (VCS) usually track the whole history of the
source code in a central server that everyone that can access. This 
central server contains all the changes and branches of the code and 
the users that can read the versions or commit changes have to connect 
to this repository. The most popular today example of this approach is SVN, which is a 
widely used VCS.

Distributed Version Control Systems (DVCS) are a modern way of managing
revisions of software that do not have a centralized server, for this reason 
they are also called De-centralized Version Control Systems. Everybody has a 
copy of the full repository with all changes made in the history.

The concept of distributed repositories came up first on the commercial product 
Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
on to design BitKeeper, another commercial VCS which expanded on those ideas. 
BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
the license to use BitKeeper was finished. 
To replace the use of BitKeeper in the Linux kernel, two projects started, Git and 
Mercurial, both now mature DVCS. Other open source DVCS in use today are Bazaar, 
developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
the idea of tracking only patches and not versions.

%Vamos a contar cuando surgió esta tecnología y sus principales 
%exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 
%similitudes con otros sistemas de versionado distribuidos como Mercurial. 
%Un poco se contará las diferencias fundamentales entre las herramientas de 
%versionado centralizadas y distribuidas, simplemente nombrando las diferencias 
%pero no explicándolas.

We're going to do a comparison between centralized and decentralized control version systems,
highlighting the differences and advantages and disadvantages of both approachs in various 
contexts, both on a conceptual and practical level. In this paper we'll base our explanations 
on Git but there are no big differences between 
most of these DVCS, especially between Git and Mercurial that are largely similar, with 
most commands having the same names in both tools.

%La idea del paper sería contar las ventajas que puede 
%tener este esquema dentro de un ambiente enterprise de código cerrado, en contraste 
%a un ambiente open source donde el esquema distribuido tiene incluso más sentido.
